Gaussian mean estimation in simulated data sets

### 2020-06-16 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

```{r load-pkgs, message=FALSE, warning=FALSE}
library(plyr)
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/signals.R")
source("../code/gaussmeanest.functions.R")
```

>>>>

```{r load-pkgs, message=FALSE, warning=FALSE}
library(plyr)
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/signals.R")
source("../code/gaussmeanest.functions.R")
theme_set(theme_cowplot())
```
